%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage{newtxtext}
\usepackage{titlesec}

% what is your name?
\newcommand{\myname}{ZHANG, Yongkang}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\titleformat{\section}
{\lsstyle\sffamily\small\bfseries\uppercase}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname} \hfill{(\textit{Last updated on: Sept. 6th, 2022})}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Department of Computer Science and Engineering \\
        Hong Kong University of Science and Technology \\
        Clear Water Bay, Hong Kong S.A.R., China
    \end{minipage}	
    \begin{minipage}[t]{0.2\textwidth}
        % contact info details, right-aligned
        %\flushright{}
        \href{mailto:yzhangne@cse.ust.hk}{yzhangne@cse.ust.hk} \\
        +86 15337296679 \\
        \href{https://ykzhang1999.github.io/}{https://ykzhang1999.github.io/}
    \end{minipage}

\section*{Research Areas}

\begin{itemize}
	
	\item \textbf{Areas:} Cloud Computing; Containers; Resource Management.
	\item \textbf{Focus:} Achieve balance between resource efficiency and high quality-of-service in large-scale data centers.
	
\end{itemize}


\section*{Education}

\textbf{Hong Kong University of Science and Technology} \hfill {Hong Kong S.A.R., China}\\
Ph.D. in Computer Science and Engineering \hfill {Sep. 2021 - Present}\\
GPA: 3.77 / 4.30; HKPFS Awardee\\
Thesis Supervisor: Prof. WANG, Wei and Prof. CHU, Xiaowen

\vspace{0.5em}
\textbf{Wuhan University} \hfill {Wuhan, Hubei, China}\\
B.Eng. in Computer Science and Technology \hfill {Sep. 2017 - Jun. 2021}\\
GPA: 3.98 / 4.00; GPA Ranking: 2 / 334; Excellent Undergraduate Thesis\\
Thesis: Idle Memory Reclamation and Overcommitment on Cloud\\
Thesis Supervisor: Prof. ZHANG, Huyin

\section*{Industrial Experience}

\textbf{Alibaba Group} \hfill {Hangzhou, Zhejiang, China}\\
Visiting Student of Cluster Management Group, CTO Line \hfill {Feb. 2022 - Present}\\
Mentor: HE, Jian

\textbf{Alibaba Cloud} \hfill {Hangzhou, Zhejiang, China}\\
Research Intern of Cluster Management Group, Cloud Native Division \hfill {Oct. 2020 - Jul. 2021}\\
Mentor: HE, Jian

\vspace{0.5em}
\textbf{Microsoft Research Asia} \hfill {Beijing, China}\\
Research Intern of Networking Research Group \hfill {Jul. 2020 - Oct. 2020}\\
Mentor: Dr. CHENG, Wenxue and Dr. CHENG, Peng


    \section*{Publications}

    %\subsection*{Journal Articles}

    %\begin{tablist}

    %    \item[2021] \tab{}Boeing, G. \enquote{Street Network Models and Indicators for Every Urban Area in the World.} \textit{Geographical Analysis}, published online ahead of print. \href{https://doi.org/10.1111/gean.12281}{doi:10.1111/gean.12281}
   % \end{tablist}

    \subsection*{Conferences}

    \begin{tablist}

        \item[2022] \tab{} \underline{\textbf{Yongkang Zhang}}, Yinghao Yu, Wei Wang, Qiukai Chen, Jie Wu, Zuowei Zhang, Jiang Zhong, Tianchen Ding, Qizhen Weng, Lingyun Yang, Cheng Wang, Jian He, Guodong Yang, and Liping Zhang, ``Workload Management in Alibaba Clusters: The Good, the Bad, and the Ugly,'' accepted to appear in \textit{the Proceedings of ACM Symposium on Cloud Computing} (\textit{\textbf{SoCC '22}}), San Francisco, CA, November 2022.
    \end{tablist}

\section*{Projects}

\textbf{Idle Memory Reclamation and Overcommitment on Cloud Container Platform}\\
A part of my work during the internship at Alibaba Group.\\
Challenges: Improve memory utilization in datacenter without undermining latency-sensitive services' quality of service.\\
My Contributions:\\
1. Developed the memory pressure detector in Alibaba's container management system.\\
2. Leveraged \textit{Memory Pressure Stall Information} to detect memory pressure brought by memory overcommitment.\\
3. Improved the memory utilization by around 10\% in multiple data centers without impacting the CPI of latency-sensitive services.

\vspace{0.5em}
\textbf{AlphaRTC (Reinforcement-learning-based Network Bandwidth Prediction in Real-time Communication)}\\
A part of my work during the internship at Microsoft Research Asia\\
Challenges: RL model's poor adaptability to different scenarios.\\
My Contributions:\\
1. Added supervised information into RL: Proposed unified reward function and classification loss to improve model performance in multiple scenarios.\\
2. Improved model's performance by 72\% in ISP scenario, 55\% in Burst Loss scenario.

\section*{Skills}

\subsection*{Language}

Chinese - Mandarin (Mother tongue); English (TOEFL: 113 / 120; CET-6: 683 / 710).

\vspace{-0.5em}
\subsection*{Programming}

C++ / C, Go, Python, Java, Verilog HDL, Tensorflow, PyTorch

\vspace{-0.5em}
\subsection*{Others}

LaTeX

\section*{Awards}

\subsection*{Awards Obtained in the Ph.D. Program}

RedBird Ph.D. Scholarship, School of Engineering, HKUST \hfill{2021}

Hong Kong Ph.D. Fellowship (\textit{Only 300 Awardees in HK}), University Grant Council \hfill{2021 - 2025}

\vspace{-0.5em}
\subsection*{Awards Obtained in the Undergraduate Program}

Excellent Undergraduate Thesis, Wuhan University \hfill{2021}

Sensetime Scholarship (Runner-up), Sensetime Group \hfill{2019}

National Scholarship, The Ministry of Education \hfill{2018}

The First Class Scholarship, Wuhan University \hfill{2018}

\vspace{-0.5em}
\subsection*{Awards Obtained in Olympiad in Informatics (Organized by China Computer Federation)}

Silver Medal, China Team Selection Competition \hfill{2016}

Silver Medal, Winter Camp of National Olympiad in Informatics \hfill{2016}

Bronze Medal, National Olympiad in Informatics  \hfill{2016}

Bronze Medal, Asia-Pacific Informatics Olympiad (China District) \hfill{2015 \& 2016}

First Prize, National Olympiad in Informatics in Provinces  \hfill{2014 \& 2015}

\end{document}
